%*******************************************************
% Abstract in English
%*******************************************************
\pdfbookmark[0]{Abstract}{Abstract}


\begin{otherlanguage}{american}
	\chapter*{Abstract}
    Business Intelligence (BI) is used in companies to analyze and visualize data. This requires applications for data integration, storage and reporting. In a current BI system, these applications run on local hardware. In the future, this system is expected to be replaced by a modern BI solution in the Azure Cloud. This raises the question of what an architecture should look like that covers all the required functionalities as cost-effectively as possible while at the same time meeting security and data protection requirements. To answer this question, various components of the Azure Cloud are evaluated in relation to a requirements specification. Based on the evaluation results, a complete concept for a new BI architecture is designed. In addition, other services are considered in the design to optimize security. The new BI architecture is implemented as a prototype that demonstrates that the cloud BI concept works in practice. The implementation will address how a potential migration could be accomplished with the least amount of effort. A final evaluation of the test cases shows that the prototype meets more requirements than the existing system.  On this basis, it will be discussed when the move from on-premise to cloud BI is worthwhile and what should be considered in the process. \end{otherlanguage}


  